---
title: "How to challenge a FMEA with historian data"
date: 2026-05-17
categories: [fmea, spc, lyo, gxp]
order: 3
execute:
  echo: false
  warning: false
  message: false
editor:
  markdown:
    wrap: sentence
---

```{r setup}
library(tidyverse)
library(gt)
library(reactable)
library(reactablefmtr)
library(dataui)
library(plotly)
library(htmltools)

fdsim_path <- here::here("..", "FDSim")
mlr_path   <- here::here("..", "machinelogR")

for (f in list.files(file.path(fdsim_path, "R"), pattern = "\\.R$", full.names = TRUE)) source(f)
devtools::load_all(mlr_path, quiet = TRUE)

cache_dir <- file.path(mlr_path, "sandbox", "fmea_connect_cache")
```

```{r load-cache}
batch_pump   <- readRDS(file.path(cache_dir, "batch_C2.rds"))
events_pump  <- readRDS(file.path(cache_dir, "events_C2.rds"))
mlog_pump    <- readRDS(file.path(cache_dir, "mlog_C2.rds"))
params       <- readRDS(file.path(cache_dir, "params.rds"))
fmea_lyo     <- readRDS(file.path(cache_dir, "fmea_lyo.rds"))
on_cycles_C2 <- readRDS(file.path(cache_dir, "on_cycles_C2.rds"))
hmm_pump_C2  <- readRDS(file.path(cache_dir, "hmm_pump_C2.rds"))

# Translate failure mode names to English and update cache
fmea_lyo <- fmea_lyo |>
  mutate(failure_mode = case_when(
    grepl("pompe",      failure_mode, ignore.case = TRUE) ~ "Vacuum pump degradation",
    grepl("condenseur", failure_mode, ignore.case = TRUE) ~ "Condenser drift (ice buildup)",
    grepl("T_crit",     failure_mode, ignore.case = TRUE) ~ "Product T_crit exceedance",
    TRUE ~ failure_mode
  ))
saveRDS(fmea_lyo, file.path(cache_dir, "fmea_lyo.rds"))

N            <- params$N
params_pump  <- params$pC2
ALARM_THRESH <- params_pump$P_ch_setpt * params_pump$pump_alarm_P_frac
STABLE_LOTS  <- params_pump$pump_stable_lots
SEED         <- params$SEED

# HMM : premier lot avec au moins un cycle dégradé
det_lot_first <- hmm_pump_C2$posterior |>
  dplyr::filter(hmm_state != hmm_pump_C2$healthy_state) |>
  dplyr::pull(lot) |>
  min()

# Durées des états HMM (depuis le cache, pas hardcodées)
.e           <- hmm_pump_C2$emission_s
dur_healthy  <- round(.e$elapsed_mean_s[.e$hmm_state == hmm_pump_C2$healthy_state])
dur_early    <- round(.e$elapsed_mean_s[.e$hmm_state == hmm_pump_C2$early_state])
dur_advanced <- round(.e$elapsed_mean_s[.e$hmm_state == hmm_pump_C2$advanced_state])
lbl_healthy  <- paste0("Healthy (", dur_healthy, " s/cycle)")
lbl_early    <- paste0("Early degradation (", dur_early, " s/cycle)")
lbl_advanced <- paste0("Advanced degradation (", dur_advanced, " s/cycle)")

# Proportions d'états par lot (pour la figure proportion)
prop_by_lot <- hmm_pump_C2$posterior |>
  dplyr::count(lot, hmm_state) |>
  dplyr::group_by(lot) |>
  dplyr::mutate(pct = n / sum(n)) |>
  dplyr::ungroup() |>
  dplyr::mutate(state_label = dplyr::case_when(
    hmm_state == hmm_pump_C2$healthy_state  ~ lbl_healthy,
    hmm_state == hmm_pump_C2$early_state    ~ lbl_early,
    hmm_state == hmm_pump_C2$advanced_state ~ lbl_advanced
  ))
```

```{r connect-pump}
res_pump <- connect_fmea_to_log(
  fmea_lyo,
  mlog(mlog_pump |> select(equipment_ID, type, alarm, start, end, elapsed_s))
)
```

With `FDSim`, the freeze-drying simulator, and `machinelogR`, the analytics package,\
let's see how we can challenge two **FMEA** scores: *Occurrence* and *Detectability*.

## The scenario

Once again, we'll simulate a **vacuum pump failure** during a freeze-drying cycle.\
With the simulator, we can set exactly when that happens and watch the effect.

The pump degradation triggers a chain reaction:

```{mermaid}
%%{init: {'theme': 'default', 'themeVariables': {'background': '#ffffff'}}}%%
flowchart LR
classDef pump    fill:#f5f5f5,stroke:#9e9e9e,color:#333
classDef rising  fill:#fff3e0,stroke:#d97706,color:#333
classDef product fill:#fffde7,stroke:#f59e0b,color:#333
classDef danger  fill:#fef2f2,stroke:#b91c1c,color:#b91c1c

A["<img src='https://api.iconify.design/material-symbols:water-pump-outline.svg' width='28' height='28'/><br/><b>Pump</b><br/>loses<br/>capacity"]:::pump -->|less<br/>vacuum| B["<img src='https://api.iconify.design/lucide:gauge.svg' width='28' height='28'/><br/><b>Chamber<br/>Pressure</b><br/>rises"]:::rising -->|with the same<br/>shelf temp.| C["<img src='https://api.iconify.design/lucide:thermometer.svg' width='28' height='28'/><br/><b>Max vial<br/>temperature</b><br/>rises"]:::product -->|approaches<br/>critical temp.| D["<img src='https://api.iconify.design/lucide:triangle-alert.svg' width='28' height='28'/><br/><b>Batch</b><br/>at risk"]:::danger
```

For this demo, I've set a **pump degradation** starting at batch **16**.\
We'll first track the mean chamber pressure (P_ch) during primary drying, across 50 batches.

## The FMEA *(Failure Mode and Effects Analysis)*

*The scores below are illustrative. They follow FMEA conventions but do not represent a validated risk assessment for any real equipment.*

```{r fmea-table}
fmea_lyo |>
  filter(grepl("pump", failure_mode, ignore.case = TRUE)) |>
  select(failure_mode, severity, occurrence, detection, rpn) |>
  gt() |>
  cols_label(failure_mode = "Failure mode", severity = "S", occurrence = "O",
             detection = "D", rpn = "RPN")
```

**S** -- severity of the effect on product quality (here: product collapse). 1--10.\
**O** -- frequency of the failure mode over equipment lifetime. 1--10.\
**D** -- likelihood of catching it before it reaches the product.

**RPN** = S x O x D  --  (Risk Priority Number)

This plausible scoring grid shows why the first guess for D *(Detectability)* is 7 :
```{r scoring-grid}
d_scale   <- scales::col_numeric(c("#d6eaf8", "#1a5276"), domain = c(1, 10))
rpn_scale <- scales::col_numeric(c("#27ae60", "#c0392b"), domain = c(0, 250))

tibble(
  D = c("9-10", "7-8", "5-6", "3-4", "1-2"),
  Criterion = c(
    "No data available",
    "Data available, but not consulted",
    "Data reviewed periodically, no trend analysis",
    "Continuous monitoring with detection rules",
    "Continuous monitoring with operational early detection"
  )
) |>
  gt() |>
  tab_style(style = list(cell_fill(color = d_scale(9.5)), cell_text(color = "white")),
            locations = cells_body(rows = D == "9-10", columns = D)) |>
  tab_style(style = list(cell_fill(color = d_scale(7.5)), cell_text(color = "white")),
            locations = cells_body(rows = D == "7-8",  columns = D)) |>
  tab_style(style = cell_fill(color = d_scale(5.5)),
            locations = cells_body(rows = D == "5-6",  columns = D)) |>
  tab_style(style = cell_fill(color = d_scale(3.5)),
            locations = cells_body(rows = D == "3-4",  columns = D)) |>
  tab_style(style = cell_fill(color = d_scale(1.5)),
            locations = cells_body(rows = D == "1-2",  columns = D))
```

A similar scoring grid for O *(Occurrence)* would depend on the equipment.\
So I chose O = 4 as a *"not too frequent"* initial guess.


## What the log reveals

The FMEA and data log are connected through this pipeline:

```{mermaid}
%%{init: {'theme': 'default', 'themeVariables': {'background': '#ffffff'}}}%%
flowchart LR
classDef data fill:#f0fdf9,stroke:#0f766e,color:#0f172a
classDef fn   fill:#eff6ff,stroke:#2563eb,color:#0f172a
classDef out  fill:#fef3c7,stroke:#d97706,color:#0f172a

A["FDSim output"]:::data --> B(["mlog()"]):::fn
C["FMEA"]:::data --> D(["connect_fmea_to_log()"]):::fn
B --> D
D --> E["n_events, last seen"]:::out
```

The log shows 8 alarm events.

```{r results-pump}
res_pump |>
  filter(grepl("pump", failure_mode, ignore.case = TRUE)) |>
  select(failure_mode, detection, rpn, n_events) |>
  gt() |>
  cols_label(failure_mode = "Failure mode", detection = "D", rpn = "RPN",
             n_events = "Alarms found")
```


```{r metrics-pump}
extract_P_ch <- function(batch) {
  map_dfr(seq_len(length(batch)), function(i) {
    prim <- batch[[i]] |> filter(phase == "primary")
    tibble(lot = i, P_ch_mean = mean(prim$P_ch, na.rm = TRUE))
  })
}

metrics_pump    <- extract_P_ch(batch_pump)
alarm_lots_pump <- events_pump |> filter(category == "Alarme") |> pull(batch_id) |> unique()
alarm_pts_pump  <- metrics_pump |> filter(lot %in% alarm_lots_pump)
```

```{r spc-setup}
ONSET <- STABLE_LOTS + 1L
RULES <- c(1L, 2L, 5L)
T_CRIT_C <- .LYO_CONST$T_crit - 273.15

metrics_all <- map_dfr(seq_len(N), function(i) {
  prim <- batch_pump[[i]] |> filter(phase == "primary")
  tibble(
    lot            = i,
    P_ch_mean      = mean(prim$P_ch,       na.rm = TRUE),
    pump_duty_mean = mean(prim$pump_duty,  na.rm = TRUE),
    T_vial_max_C   = max(prim$T_vial_C,   na.rm = TRUE)
  )
})

bl <- metrics_all |> filter(lot <= STABLE_LOTS)

make_lim <- function(col) spc_baseline(
  bl |> rename(value = !!col), variable = "value", time_col = "lot"
)

lim_P    <- make_lim("P_ch_mean")
lim_pump <- make_lim("pump_duty_mean")

fl_phase2 <- function(det) {
  idx <- det$first_index[det$detected & !is.na(det$first_index) & det$first_index > STABLE_LOTS]
  if (length(idx) == 0) return(list(lot = NA_integer_, lag = NA_integer_, rule = NA_integer_))
  lot  <- min(idx)
  rule <- det$rule[det$first_index == lot & det$detected][1]
  list(lot = lot, lag = lot - ONSET, rule = rule)
}

det_P    <- first_detection(metrics_all$P_ch_mean,      lim_P,    RULES)
det_pump <- first_detection(metrics_all$pump_duty_mean, lim_pump, RULES)

fl_P    <- fl_phase2(det_P)
fl_pump <- fl_phase2(det_pump)

alarm_first <- events_pump |> filter(category == "Alarme") |> pull(batch_id) |> min()

pump_row <- fmea_lyo |> filter(grepl("pump", failure_mode, ignore.case = TRUE))
S_pump   <- pump_row$severity[1]
O_pump   <- pump_row$occurrence[1]
```

```{r theme}
theme_web <- theme_minimal(base_size = 13) +
  theme(
    panel.grid.minor  = element_blank(),
    panel.grid.major  = element_line(colour = "grey92", linewidth = 0.3),
    plot.title        = element_text(face = "bold", size = 14),
    plot.subtitle     = element_text(colour = "grey40", size = 11),
    axis.text         = element_text(size = 11),
    axis.title        = element_text(size = 12),
    plot.caption      = element_text(size = 9, colour = "grey55", hjust = 0),
    plot.background   = element_rect(fill = "white", colour = NA),
    panel.background  = element_rect(fill = "white", colour = NA)
  )
```

```{r fig-pump, fig.width=8, fig.height=5}
ggplot(metrics_pump, aes(lot, P_ch_mean)) +
  geom_vline(xintercept = STABLE_LOTS + 0.5, colour = "grey65", linetype = "dashed", linewidth = 0.5) +
  annotate("text", x = STABLE_LOTS + 0.8, y = 16,
           label = "Pump degradation onset (batch 16)", hjust = 0, size = 3.2, colour = "grey50") +
  geom_hline(yintercept = ALARM_THRESH, colour = "#c0392b", linetype = "dashed", linewidth = 0.7) +
  annotate("text", x = 2, y = ALARM_THRESH + 0.25,
           label = sprintf("Alarm threshold %.0f Pa", ALARM_THRESH),
           hjust = 0, size = 3.2, colour = "#c0392b") +
  geom_line(colour = "#e67e22", linewidth = 0.8) +
  geom_point(data = alarm_pts_pump, aes(lot, P_ch_mean),
             colour = "#c0392b", size = 3, shape = 16) +
  annotate("text",
           x = min(alarm_lots_pump) + 0.8,
           y = alarm_pts_pump |> filter(lot == min(alarm_lots_pump)) |> pull(P_ch_mean) + 0.3,
           label = paste0("First alarm\nbatch ", min(alarm_lots_pump)),
           hjust = 0, size = 3.2, colour = "#c0392b", lineheight = 0.9) +
  annotate("segment",
           x = STABLE_LOTS + 0.5, xend = min(alarm_lots_pump) - 0.5,
           y = 9, yend = 9,
           colour = "grey45", linewidth = 0.5,
           arrow = arrow(ends = "both", type = "closed", length = unit(0.15, "cm"))) +
  annotate("text",
           x = (STABLE_LOTS + min(alarm_lots_pump)) / 2, y = 9.35,
           label = "22 batches running blind", size = 3, colour = "grey45", hjust = 0.5) +
  scale_y_continuous(limits = c(8.5, NA)) +
  scale_x_continuous(breaks = c(1, 10, 20, 30, 40, 50)) +
  labs(x = "Batch", y = "Mean P_ch (Pa)",
       caption = sprintf("FDSim seed=%d | machinelogR::connect_fmea_to_log()", SEED)) +
  theme_web
```

Chamber pressure crosses the alarm threshold at batch 38: [22 batches]{.problem} after onset.



## Updated FMEA

Now that the data log has been connected, the risk can be reevaluated.

**D -- Detectability:**\
D was 7 because the historian was not consulted.\
We can now set D=6 (band 5-6): the log is periodically reviewed, but there's still no trending.

**O -- Occurrence:**\
The pipeline revealed `n_events / total_batches`  =  8 alarm events over 50 batches  =  **16%**.\
The declared O=4 was an expert estimate.\
The log now puts a number on it, but how acceptable is 16%? Unfortunately, without a reliable scoring grid, I'll leave O=4 for the rest of this demo. With a scoring grid, O could be better than expected... or worse.

Now with a D=6 and O=4, the RPN drops from 196 to 168.

```{r fmea-updated}
pump_raw <- res_pump |>
  filter(grepl("pump", failure_mode, ignore.case = TRUE))

fmea_updated <- pump_raw |>
  select(failure_mode, severity, occurrence, detection, rpn, n_events) |>
  mutate(
    occurrence_note = paste0(n_events, " events / ", N, " batches"),
    detection       = 6L,
    rpn             = severity * occurrence * detection
  )

fmea_updated |>
  select(failure_mode, severity, occurrence, occurrence_note, detection, rpn) |>
  gt() |>
  tab_style(
    style = list(cell_fill(color = "#E8F5E9"), cell_text(weight = "bold")),
    locations = cells_body(columns = c(detection, rpn))
  ) |>
  tab_style(
    style = list(cell_fill(color = "#EFF6FF")),
    locations = cells_body(columns = c(occurrence, occurrence_note))
  ) |>
  cols_label(
    failure_mode    = "Failure mode",
    severity        = "S",
    occurrence      = "O",
    occurrence_note = "Observed rate",
    detection       = "D",
    rpn             = "RPN"
  )
```



Can we further improve the *Detectability* D ?\


## Deeper in the monitoring stack

D moves down in steps. Method first, then signal position in the failure chain, then observation window. Each lever is independent.

### SPC on chamber pressure

The control limits are calculated from the first 15 stable batches (Phase I baseline).

```{r fig-spc-pch, fig.width=8, fig.height=3}
UCL_P <- lim_P$CL + 3 * lim_P$sigma
rng_P <- diff(range(metrics_all$P_ch_mean))
p_pch <- ggplot(metrics_all, aes(lot, P_ch_mean)) +
  geom_vline(xintercept = STABLE_LOTS + 0.5, colour = "grey65", linetype = "dashed", linewidth = 0.5) +
  geom_hline(yintercept = lim_P$CL, colour = "grey55", linetype = "solid", linewidth = 0.5) +
  geom_hline(yintercept = UCL_P, colour = "#c0392b", linetype = "dashed", linewidth = 0.7) +
  annotate("text", x = 2, y = UCL_P + rng_P * 0.07,
           label = sprintf("UCL %.1f Pa", UCL_P),
           hjust = 0, size = 3.2, colour = "#c0392b") +
  annotate("text", x = 2, y = lim_P$CL + rng_P * 0.05,
           label = sprintf("CL %.1f Pa", lim_P$CL),
           hjust = 0, size = 3.0, colour = "grey45") +
  geom_line(colour = "#2980b9", linewidth = 0.8) +
  scale_x_continuous(breaks = c(1, 10, 20, 30, 40, 50)) +
  labs(x = "Batch", y = "Mean P_ch (Pa)") +
  theme_web
if (!is.na(fl_P$lot)) {
  det_pt_P <- metrics_all |> filter(lot == fl_P$lot)
  p_pch <- p_pch +
    geom_vline(xintercept = fl_P$lot, colour = "#c0392b", linetype = "dotted", linewidth = 0.8) +
    geom_point(data = det_pt_P, aes(x = lot, y = P_ch_mean),
               colour = "#c0392b", size = 5, shape = 18)
}
p_pch
```

[Detection at batch `r fl_P$lot`]{.solution} after 9 consecutive batches above the center line (rule 2).\
That's **`r fl_P$lag` batches after onset**.\
Detectability D can now be lowered to 4 (Continuous monitoring with detection rules).

### SPC on pump duty cycle

Let's look at the pump cycle instead of the chamber pressure. It's the % time the pump runs per batch.\
When capacity degrades, the pump compensates by running longer.

```{r fig-spc-pump, fig.width=8, fig.height=3}
UCL_pump <- lim_pump$CL + 3 * lim_pump$sigma
rng_pump <- diff(range(metrics_all$pump_duty_mean))
p_pump <- ggplot(metrics_all, aes(lot, pump_duty_mean)) +
  geom_vline(xintercept = STABLE_LOTS + 0.5, colour = "grey65", linetype = "dashed", linewidth = 0.5) +
  geom_hline(yintercept = lim_pump$CL, colour = "grey55", linetype = "solid", linewidth = 0.5) +
  geom_hline(yintercept = UCL_pump, colour = "#c0392b", linetype = "dashed", linewidth = 0.7) +
  annotate("text", x = 2, y = UCL_pump + rng_pump * 0.07,
           label = sprintf("UCL %.3f", UCL_pump),
           hjust = 0, size = 3.2, colour = "#c0392b") +
  annotate("text", x = 2, y = lim_pump$CL + rng_pump * 0.05,
           label = sprintf("CL %.3f", lim_pump$CL),
           hjust = 0, size = 3.0, colour = "grey45") +
  geom_line(colour = "#8e44ad", linewidth = 0.8) +
  scale_x_continuous(breaks = c(1, 10, 20, 30, 40, 50)) +
  labs(x = "Batch", y = "Pump duty (fraction ON)") +
  theme_web
if (!is.na(fl_pump$lot)) {
  det_pt_pump <- metrics_all |> filter(lot == fl_pump$lot)
  p_pump <- p_pump +
    geom_vline(xintercept = fl_pump$lot, colour = "#c0392b", linetype = "dotted", linewidth = 0.8) +
    geom_point(data = det_pt_pump, aes(x = lot, y = pump_duty_mean),
               colour = "#c0392b", size = 5, shape = 18)
}
p_pump
```

[Detection at batch `r fl_pump$lot`]{.solution}, **`r fl_pump$lag` batches after onset**, the earliest in this simulation.\
The Detectability D has improved and can now be lowered to 3.

### Intra-cycle signals

Every pump ON/OFF event is recorded.

The function `fit_hmm()` fits a Hidden Markov Model on the sequence of ON-cycle durations.\
It identifies 3 *latent states* based on ON-cycle duration: healthy (`r dur_healthy` s/cycle), early degradation (`r dur_early` s/cycle), or advanced degradation (`r dur_advanced` s/cycle).\
The chart shows the % of each state per batch.

```{r fig-hmm-pump, fig.width=8, fig.height=4}
state_order_bar <- c(lbl_healthy, lbl_early, lbl_advanced)
state_cols_bar  <- setNames(
  c("#27ae60", "#e67e22", "#8e44ad"),
  c(lbl_healthy, lbl_early, lbl_advanced)
)

ggplot(
  prop_by_lot |>
    dplyr::mutate(state_label = factor(state_label, levels = state_order_bar)),
  aes(lot, pct, fill = state_label)
) +
  geom_col(width = 0.9, alpha = 0.72) +
  geom_vline(xintercept = STABLE_LOTS + 0.5, colour = "grey65",
             linetype = "dashed", linewidth = 0.5) +
  geom_vline(xintercept = det_lot_first - 0.5, colour = "#c0392b",
             linetype = "dotted", linewidth = 0.8) +
  scale_fill_manual(values = state_cols_bar) +
  scale_x_continuous(breaks = c(1, 10, 20, 30, 40, 50)) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = "Batch", y = "% of ON-cycles", fill = NULL,
       caption = sprintf(
         "Grey dashed: degradation onset (batch %d). Red dotted: first degraded cycles (batch %d).",
         STABLE_LOTS + 1L, det_lot_first
       )) +
  theme_web +
  theme(legend.position = "bottom")
```

[First degraded cycles at batch `r det_lot_first`]{.solution}, **`r det_lot_first - ONSET` batches after onset.**\
The HMM assigns individual ON-cycles to a degraded state as soon as the pump capacity drops significantly.\
The Detectability D drops to 2.

### Conclusion

O could not be updated. But how much did D move?

```{r tbl-recap}
recap_tbl <- tibble(
  Step             = c("Initial guess", "+ data",           "+ SPC",          "+ SPC",         "+ HMM"),
  Step_highlight   = c(0,               1,                  1,                0,               1),
  Signal           = c("(none)",        "P_ch",             "P_ch",           "Pump duty",     "T_ON duration"),
  Signal_highlight = c(0,               1,                  0,                1,               1),
  Trigger          = c("",              "Alarm threshold",  "Nelson rule 2",  "Nelson rule 1", "HMM state change"),
  Trigger_highlight= c(0,               0,                  1,                0,               1),
  `Detection at batch` = c("", min(alarm_lots_pump), fl_P$lot, fl_pump$lot, det_lot_first),
  D        = c(7L, 6L, 4L, 3L, 2L),
  RPN      = S_pump * O_pump * c(7L, 6L, 4L, 3L, 2L),
  D_color  = d_scale(c(7L, 6L, 4L, 3L, 2L)),
  RPN_color = rpn_scale(S_pump * O_pump * c(7L, 6L, 4L, 3L, 2L))
)

pill <- function(value) {
  span(
    style = "
      background: #8fbc8f;
      color: white;
      font-weight: 500;
      border-radius: 12px;
      padding: 2px 10px;
      display: inline-block;
    ",
    value
  )
}

pill_if <- function(flag_col) {
  function(value, index) {
    if (recap_tbl[[flag_col]][index] == 1) pill(value) else value
  }
}

reactable(
  recap_tbl |> select(-D_color, -RPN_color, -Signal_highlight, -Step_highlight, -Trigger_highlight),
  columns = list(
    `Detection at batch` = colDef(),
    Step = colDef(cell = pill_if("Step_highlight")),
    Signal  = colDef(minWidth = 120, cell = pill_if("Signal_highlight")),
    Trigger = colDef(minWidth = 160, cell = pill_if("Trigger_highlight")),
    D = colDef(
      minWidth = 100,
      cell = data_bars(recap_tbl, fill_color_ref = "D_color", fill_gradient = FALSE,
                       bar_height = 16, text_position = "outside-end",
                       min_value = 1, max_value = 10)
    ),
    RPN = colDef(
      minWidth = 100,
      cell = data_bars(recap_tbl, fill_color_ref = "RPN_color", fill_gradient = FALSE,
                       bar_height = 16, text_position = "outside-end",
                       min_value = 0, max_value = 250)
    )
  ),
  highlight  = TRUE,
  borderless = TRUE,
  theme = reactableTheme(backgroundColor = "white", highlightColor = "#fafafa",
                         cellPadding = "8px 12px")
)
```

From D=7 to D=2, the RPN dropped from `r S_pump * O_pump * 7L` to `r S_pump * O_pump * 2L`, without touching Severity or Occurrence.\
Just by improving the monitoring method.\
The closer the signal to the failure mechanism, the earlier the detection.
